A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-07-24 tidyindex.qmd
write up for the gggi index section

Indexes are commonly-used tools to monitor, communicate and make decisions across various domains in society. Their applications can be found in the environment (e.g. Air Quality Index, El Niño-Southern Oscillation Index), in the economy (Consumer Price Index, stock market indexes), and in the social sciences (e.g. QS University Rankings, Human Development Index).

To construct an index, experts typically first define an underlying concept of interest to measure, then collect relevant variables for measuring the concept, and lastly summarise these variables into a single numerical or categorical value. An index can be as simple as counting the number of days when the maximum temperature is greater than 25 degree. This is "the number of summer days" (SU), a climate index listed in ETCCDI Climate Change Indices [@climate-indexes]. In some cases, indexes are weighted linear combinations of variables. For example, Human Development Index (HDI) [@hdi] combines the three aspects (life expectancy, years of schooling, and GNI per capita) to measure country's development. In more complex scenarios, indexes are constructed by combining multiple variables, often accompanied by spatial and temporal considerations arising from diverse data formats, including in-situ stations, satellite imageries, and model outputs. An example of this is the Combined Drought Index (CDI) [@cdi], curated by the European Drought Observatory, which uses a decision tree to combine Standardized Precipitation Index (SPI) [@spi] with the satellite measure, Fraction of Absorbed Photosynthetically Active Radiation (FAPAR), and modelled soil moisture.

@@

@@

```{r gggi-verify}
set.seed(123)
n <- 1000
w_idx <- map(1:n, function(x){
  w_idx <- stats::runif(4, min = 0.1, max = 1)
  w_idx <- w_idx/sum(w_idx)
  w_idx %>% as.matrix(nrow = 4, ncol = 1)
  })
rand_w <- reduce(w_idx, cbind) %>% as_tibble()
colnames(rand_w) <- paste0("V", 1:n)

dim_weights <- gggi_weights %>%
  filter(!is.na(pillar_weight)) %>%
  select(variable, pillar_weight) %>% 
  bind_cols(rand_w)

dt <- gggi %>% 
  select(country:political_empowerment) %>% 
  init(id = country) %>%
  add_meta(dim_weights, var_col = variable)

dt2 <- dt %>%
  dimension_reduction(
    index_new = aggregate_linear(
      ~economic_participation_and_opportunity:political_empowerment,
      weight = pillar_weight))

dt2$data %>%
  ggplot(aes(x = index, y = index_new)) +
  geom_abline(slope = 1, intercept = 0, color = "grey") + 
  geom_point() +
  theme_bw() + 
  theme(aspect.ratio = 1, panel.grid.minor = element_blank()) 
```

```{r gggi-weights, fig.height=20, fig.align='center', fig.width=10}
dt3 <- dt2 %>%
  swap_values(.id = 1, .param = weight,
              .value = list(pillar_weight, paste0("V", 2:100)),
              .raw_data = dt)

@@

@@

```{r idx-tour, fig.align='center', fig.height= 12, fig.width=12}
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at [vimeo link]."
frames <- c("001", "013", "037", "061", "085")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 3) 
```

>>>>

Indexes are commonly used to combine multivariate information into a single number for monitoring, communicating, and decision-making across various domains in society. Their applications can be found in the environment (e.g. Air Quality Index, El Niño-Southern Oscillation Index), in the economy (Consumer Price Index, stock market indexes), and in the social sciences (e.g. QS University Rankings, Human Development Index).

To construct an index, experts typically first define an underlying concept of interest to measure, then collect relevant variables for measuring the concept, and lastly summarise these variables into a single numerical or categorical value. Many decisions are factored into this process and

An index can be as simple as counting the number of days when the maximum temperature is greater than 25 degree. This is "the number of summer days" (SU), a climate index listed in ETCCDI Climate Change Indices [@climate-indexes]. In some cases, indexes are weighted linear combinations of variables. For example, Human Development Index (HDI) [@hdi] combines the three aspects (life expectancy, years of schooling, and GNI per capita) to measure country's development. In more complex scenarios, indexes are constructed by combining multiple variables, often accompanied by spatial and temporal considerations arising from diverse data formats, including in-situ stations, satellite imageries, and model outputs. An example of this is the Combined Drought Index (CDI) [@cdi], curated by the European Drought Observatory, which uses a decision tree to combine Standardized Precipitation Index (SPI) [@spi] with the satellite measure, Fraction of Absorbed Photosynthetically Active Radiation (FAPAR), and modelled soil moisture.

@@

Global Gender Gap Index (GGGI) [@WEF2023] is published by the World Economic Forum to measure the gender parity of 146 countries across four dimensions: Economic Participation and Opportunity, Educational Attainment, Health and Survival, and Political Empowerment. The index is expressed as a percentage and can be interpreted as the percentage of the gender gap that has been closed. Fourteen variables from the four dimensions are collected for both genders and calculated as females-to-males ratios. Within each dimension, variables are linear aggregated with weights shown in @tbl-gggi-weights. The weights is determined so that a one percentage point change in the standard deviation of each variable contributes equally to the index and is calculated as taking the inverse of the standard deviation of each variable and scaling them to sum to 1 within each dimension. The four dimensions are then aggregated with equal weights (0.25) into the final index. The 2023 GGGI data is available in the country's economy profile from the Global Gender Gap Report 2023 [@WEF2023] and can be accessed through the `tidyindex` package as `gggi`, along with the corresponding weights `gggi_weights`.

```{r tbl-gggi-weights}
#| tbl-cap: Weights of the fourteen variables in Global Gender Gap Index
#| tbl-cap-location: bottom
gggi_weights %>%  
   mutate(variable = str_replace_all(variable, "_", " ") %>%
            str_to_sentence()) %>% 
  select(c(1,2, 5:7)) %>% 
  mutate(dimension = c(rep("Economy", 5), rep("Education" ,4), 
                       rep("Health", 2), rep("Politics", 3))) %>% 
  set_names(str_to_sentence) %>% 
  knitr::kable(digits = 3)
```

A natural thing to do when provided with the index data is to reproduce the index using the described methodology to verify the index calculation. In the case of GGGI, the construction can be simplified as a single linear aggregation with variable weight (rescaled inverse of variable standard deviation) multiplied by the dimension weight (0.25 for all dimensions):

````
gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight)) 
````

The result can be compared with the GGGI values available from the report as shown in @fig-compare-gggi, validating the reproducibility of the index from the country data.

@@

```{r fig-compare-gggi}
#| fig-cap: "Verifying the calculation of the Global Gender Gap Index (GGGI). The index can be reproduced from the methodology described in the Global Gender Gap Report 2023 after removing the countries with missing variables, the treatment of which is unclear."
set.seed(123)
n <- 1000
w_idx <- map(1:n, function(x){
  w_idx <- stats::runif(4, min = 0.1, max = 1)
  w_idx <- w_idx/sum(w_idx)
  w_idx %>% as.matrix(nrow = 4, ncol = 1)
  })
rand_w <- reduce(w_idx, cbind) %>% as_tibble()
colnames(rand_w) <- paste0("V", 1:n)

dt2 <- gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight))

dt2$data %>%
  filter(!is.na(index_new)) %>% 
  ggplot(aes(x = index, y = index_new)) +
  geom_abline(slope = 1, intercept = 0, color = "grey") + 
  geom_point() +
  theme_bw() + 
  theme(aspect.ratio = 1, panel.grid.minor = element_blank()) + 
  xlab("Benchmark") + 
  ylab("Index calculated")
```

```{r eval = FALSE, gggi-weights, fig.height=20, fig.align='center', fig.width=10}
dt3 <- dt2 %>%
  swap_values(.id = 1, .param = weight,
              .value = list(pillar_weight, paste0("V", 2:100)),
              .raw_data = dt)

@@

Index analysts could be interested in understanding how the index values and country ranking change when the weights assigned the each dimension is slightly changed. This can help assess the sensitivity of the country ranking, test the robustness of the indexes to different variables, and identify the strengths and weaknesses of countries in each aspect. We run a local tour focusing on the four dimensions of countries in the South Asia and Sub-Saharan Africa region. The local tour generates an animation starting with an equal weight of 0.25 for all four dimensions and gradually increases and reduces the weight of one variable at a time. In @fig-idx-tour, we select five frames from the tour animation: the first frame represents equal weights, and the subsequent four frames have a higher weight for each of the four dimensions. When health receives a higher weight, the impact on the index value is minimal. Index values and ranking change slightly when the dimension economy and education are given a greater weight, highlighting countries with a relatively better (moving right) or worse (moving left) in these single dimensions. For example, when economy is given a higher weight, the index moves to the left for Ethiopia and Senegal, revealing it as a weakness for these two countries to improve compared to their peers with similar rankings. These information will not be observed when using a single equal weight scheme since the advantageous and disadvantageous dimension of a country will be averaged out.

Notably, increasing the weight of the politics dimension leads to a pronounced decrease of index value for almost all the countries. This can further impact the interpretation on how much of the gender gap has been closed. Analysts need to further consider the robustness of the index and potentially investigate the construction of the politics dimension, including the variable selection process.

@@

```{r fig-idx-tour, fig.align='center', fig.height= 12, fig.width=12}
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at [vimeo link]."
frames <- c("001", "013", "037", "061", "085")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 3) 
```

### 2023-07-24 tidyindex.tex
write up for the gggi index section

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Indexes are commonly-used tools to monitor, communicate and make
decisions across various domains in society. Their applications can be
found in the environment (e.g.~Air Quality Index, El Niño-Southern
Oscillation Index), in the economy (Consumer Price Index, stock market
indexes), and in the social sciences (e.g.~QS University Rankings, Human
Development Index).

To construct an index, experts typically first define an underlying
concept of interest to measure, then collect relevant variables for
measuring the concept, and lastly summarise these variables into a
single numerical or categorical value. An index can be as simple as
counting the number of days when the maximum temperature is greater than
25 degree. This is ``the number of summer days'' (SU), a climate index
listed in ETCCDI Climate Change Indices (Zhang 2020). In some cases,
indexes are weighted linear combinations of variables. For example,
Human Development Index (HDI) (United Nations Development Programme
2022) combines the three aspects (life expectancy, years of schooling,
and GNI per capita) to measure country's development. In more complex
scenarios, indexes are constructed by combining multiple variables,
often accompanied by spatial and temporal considerations arising from
diverse data formats, including in-situ stations, satellite imageries,
and model outputs. An example of this is the Combined Drought Index
(CDI) (Sepulcre-Canto et al. 2012), curated by the European Drought
Observatory, which uses a decision tree to combine Standardized
Precipitation Index (SPI) (McKee, Doesken, and Kleist 1993) with the
satellite measure, Fraction of Absorbed Photosynthetically Active
Radiation (FAPAR), and modelled soil moisture.

@@

\includegraphics{tidyindex_files/figure-pdf/gggi-verify-1.pdf}

@@

{\centering \includegraphics{tidyindex_files/figure-pdf/gggi-weights-1.pdf}

@@

@@

@@

{\centering \includegraphics{tidyindex_files/figure-pdf/idx-tour-1.pdf}

@@

\caption{Five frames selected from varying the linear weights of four
dimensions in Global Gender Gap Index. The weights vary slightly from
the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe
how the index and ranking reponse. Full animation is available at
{[}vimeo link{]}.}

@@

>>>>

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Indexes are commonly used to combine multivariate information into a
single number for monitoring, communicating, and decision-making across
various domains in society. Their applications can be found in the
environment (e.g.~Air Quality Index, El Niño-Southern Oscillation
Index), in the economy (Consumer Price Index, stock market indexes), and
in the social sciences (e.g.~QS University Rankings, Human Development
Index).

To construct an index, experts typically first define an underlying
concept of interest to measure, then collect relevant variables for
measuring the concept, and lastly summarise these variables into a
single numerical or categorical value. Many decisions are factored into
this process and

An index can be as simple as counting the number of days when the
maximum temperature is greater than 25 degree. This is ``the number of
summer days'' (SU), a climate index listed in ETCCDI Climate Change
Indices (Zhang 2020). In some cases, indexes are weighted linear
combinations of variables. For example, Human Development Index (HDI)
(United Nations Development Programme 2022) combines the three aspects
(life expectancy, years of schooling, and GNI per capita) to measure
country's development. In more complex scenarios, indexes are
constructed by combining multiple variables, often accompanied by
spatial and temporal considerations arising from diverse data formats,
including in-situ stations, satellite imageries, and model outputs. An
example of this is the Combined Drought Index (CDI) (Sepulcre-Canto et
al. 2012), curated by the European Drought Observatory, which uses a
decision tree to combine Standardized Precipitation Index (SPI) (McKee,
Doesken, and Kleist 1993) with the satellite measure, Fraction of
Absorbed Photosynthetically Active Radiation (FAPAR), and modelled soil
moisture.

@@

Global Gender Gap Index (GGGI) (World Economic Forum 2023) is published
by the World Economic Forum to measure the gender parity of 146
countries across four dimensions: Economic Participation and
Opportunity, Educational Attainment, Health and Survival, and Political
Empowerment. The index is expressed as a percentage and can be
interpreted as the percentage of the gender gap that has been closed.
Fourteen variables from the four dimensions are collected for both
genders and calculated as females-to-males ratios. Within each
dimension, variables are linear aggregated with weights shown in
Table~\ref{tbl-gggi-weights}. The weights is determined so that a one
percentage point change in the standard deviation of each variable
contributes equally to the index and is calculated as taking the inverse
of the standard deviation of each variable and scaling them to sum to 1
within each dimension. The four dimensions are then aggregated with
equal weights (0.25) into the final index. The 2023 GGGI data is
available in the country's economy profile from the Global Gender Gap
Report 2023 (World Economic Forum 2023) and can be accessed through the
\texttt{tidyindex} package as \texttt{gggi}, along with the
corresponding weights \texttt{gggi\_weights}.

\hypertarget{tbl-gggi-weights}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.5185}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1235}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1358}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1358}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0864}}@{}}
\caption{\label{tbl-gggi-weights}Weights of the fourteen variables in
Global Gender Gap Index}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimension
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Var\_weight
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Dim\_weight
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Weight
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Variable
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimension
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Var\_weight
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Dim\_weight
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Weight
\end{minipage} \\
\midrule()
\endhead
Labour force participation & Economy & 0.199 & 0.25 & 0.050 \\
Wage equality for similar work & Economy & 0.310 & 0.25 & 0.078 \\
Estimated earned income & Economy & 0.221 & 0.25 & 0.055 \\
Legislators senior officials and managers & Economy & 0.149 & 0.25 &
0.037 \\
Professional and technical workers & Economy & 0.121 & 0.25 & 0.030 \\
Literacy rate & Education & 0.191 & 0.25 & 0.048 \\
Enrolment in primary education & Education & 0.459 & 0.25 & 0.115 \\
Enrolment in secondary education & Education & 0.230 & 0.25 & 0.058 \\
Enrolment in tertiary education & Education & 0.121 & 0.25 & 0.030 \\
Sex ratio at birth & Health & 0.693 & 0.25 & 0.173 \\
Healthy life expectancy & Health & 0.307 & 0.25 & 0.077 \\
Women in parliament & Politics & 0.310 & 0.25 & 0.078 \\
Women in ministerial positions & Politics & 0.247 & 0.25 & 0.062 \\
Years with female head of state & Politics & 0.443 & 0.25 & 0.111 \\
\bottomrule()
\end{longtable}

A natural thing to do when provided with the index data is to reproduce
the index using the described methodology to verify the index
calculation. In the case of GGGI, the construction can be simplified as
a single linear aggregation with variable weight (rescaled inverse of
variable standard deviation) multiplied by the dimension weight (0.25
for all dimensions):

\begin{verbatim}
gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight)) 
\end{verbatim}

The result can be compared with the GGGI values available from the
report as shown in Figure~\ref{fig-compare-gggi}, validating the
reproducibility of the index from the country data.

@@

{\centering \includegraphics{tidyindex_files/figure-pdf/fig-compare-gggi-1.pdf}

@@

\caption{\label{fig-compare-gggi}Verifying the calculation of the Global
Gender Gap Index (GGGI). The index can be reproduced from the
methodology described in the Global Gender Gap Report 2023 after
removing the countries with missing variables, the treatment of which is
unclear.}

@@

Index analysts could be interested in understanding how the index values
and country ranking change when the weights assigned the each dimension
is slightly changed. This can help assess the sensitivity of the country
ranking, test the robustness of the indexes to different variables, and
identify the strengths and weaknesses of countries in each aspect. We
run a local tour focusing on the four dimensions of countries in the
South Asia and Sub-Saharan Africa region. The local tour generates an
animation starting with an equal weight of 0.25 for all four dimensions
and gradually increases and reduces the weight of one variable at a
time. In Figure~\ref{fig-idx-tour}, we select five frames from the tour
animation. The first frame represents equal weights, and the subsequent
four frames have a higher weight for each of the four dimensions. When
health receives a higher weight, the impact on the index value is
minimal. Index values and ranking change slightly when the dimension
economy and education are given a greater weight, highlighting countries
with a relatively better (moving right) or worse (moving left) in these
single dimensions. For example, when economy is given a higher weight,
the index moves to the left for Ethiopia and Senegal, revealing it as a
weakness for these two countries to improve compared to their peers with
similar rankings. These information will not be observed when using a
single equal weight scheme since the advantageous and disadvantageous
dimension of a country will be averaged out.

Notably, increasing the weight of the politics dimension leads to a
pronounced decrease of index value for almost all the countries. This
can further impact the interpretation on how much of the gender gap has
been closed. Analysts need to further consider the robustness of the
index and potentially investigate the construction of the politics
dimension, including the variable selection process.

@@

{\centering \includegraphics{tidyindex_files/figure-pdf/fig-idx-tour-1.pdf}

@@

\caption{\label{fig-idx-tour}Five frames selected from varying the
linear weights of four dimensions in Global Gender Gap Index. The
weights vary slightly from the official simple average weights (0.25,
0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full
animation is available at {[}vimeo link{]}.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-WEF2023}{}}%
World Economic Forum. 2023. {``{The Global Gender Gap Report 2023}.''}
\url{https://www3.weforum.org/docs/WEF_GGGR_2023.pdf}.
